---
title: "Corpus_Descriptives"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(scales)
library(data.table)

```

## Count Volumn of Results by Month
```{r results}
mydata = fread("meta_new.csv") #fread is faster

# remove duplicates
deduped.data <- distinct(mydata, Title, WordLength, .keep_all = TRUE) #based in title and word count

# format the date
deduped.data$Date = gsub("^(.*?)T.*", "\\1", deduped.data$Date) # delete hours
deduped.data$Date = as.POSIXct(deduped.data$Date)

ggplot(deduped.data, aes(x = Date)) + 
    geom_histogram() +
    theme_bw() + xlab(NULL) +
    scale_x_datetime(breaks = date_breaks("1 months"),
                    labels = date_format("%Y-%b"), 
                     limits = c(as.POSIXct("2007-01-01"), 
                                as.POSIXct("2009-12-31")) 
                    ) + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


## Count the Number of Words Over Time 

```{r words, echo=FALSE}
# setwd("/Users/yuchenluo/Desktop/forecast_downturn/txt") 
# 
# ## get rid of duplicates
# # uniq_id = deduped.data$ResultId 
# # files =  paste(uniq_id, "txt",sep = ".")
# # all_files = list.files(path="/Users/yuchenluo/Desktop/forecast_downturn/txt",pattern = "*.txt")
# # files_tbl = read.table(text = files) 
# # all_files_tbl = read.table(text =all_files)
# # deduped_file = inner_join(files_tbl, all_files_tbl)
# 
# ## get the zero counts
# zero_wc_id = deduped.data[deduped.data$WordLength==0, "ResultId"]
# #zero_wc_id = as.character(zero_wc_id)
# zero_wc_fl =  unlist(lapply(zero_wc_id, function(x) paste(x,'.txt', sep = "")))
# 
# 
# # some files do not exist in the txt folder
# all_files = list.files(path="/Users/yuchenluo/Desktop/forecast_downturn/txt",pattern = "*.txt")
# final_fl = intersect(zero_wc_fl, all_files)
# 
# # count (regex get rid of tags)
# wd_ct = sapply(final_fl, function(x){
#     t <- read_file(x) # load file
#     lst <- str_extract_all(t, "<bodyText>\\s*(.*?)\\s*</bodyText>")
#     str = paste(lst, collapse = " ") 
#     str = gsub("<[^>]*?>", "",str) # delete string inside <>
#     # [^>] means all characters except for >
#     # *? nongreedy matching: match the shortest string
#     # <> not special character donot need escape
#     WordLen = sapply(strsplit(str, " "), length)
# return(WordLen)
# })
# 
# # get rid of ext to match ResultId
# names = tools::file_path_sans_ext(names(wd_ct))
# 
# #prepare two data frames
# setDT(mydata)
# wd_ct = setDT(as.data.frame(wd_ct))
# wd_ct$ResultId = names
# 
# #mydata[which(mydata$ResultId %in% names(wd_ct)), 'WordLength'] = wd_ct
# 
# # merge
# newdata = left_join(mydata,wd_ct)
# 
# #change zero word length
# newdata[!is.na(newdata$wd_ct), "WordLength" ] = newdata[!is.na(newdata$wd_ct), "wd_ct" ]
# newdata$wd_ct = NULL
# 
# # write to file 
# write.csv(newdata, file = "meta_new.csv")
```


```{r word count over time}
ggplot(deduped.data,aes(x=Date, y=WordLength)) + geom_point(colour = "grey") +     
    stat_summary(aes(y = WordLength,group=1, shape = "median"), fun.y=median, colour="red", size = 1, geom="smooth",group=1, show.legend = TRUE)   +      scale_shape_manual("", values=c("mean"="x")) +
 coord_cartesian(ylim = c(0, 20000)) 

```
```{r words3}
ggplot(deduped.data, aes(x = WordLength)) + 
    geom_histogram(binwidth = 100) +
    xlim(c(0, 2000))
    # theme_bw() + xlab(NULL) +
    #scale_x_datetime(limits = c(as.POSIXct("2007-01-01"), 
      #                          as.POSIXct("2009-12-31")) ) 
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))```

```

## Zero Word Count Articles: Sources

```{r WordCount - zero count sources}
ggplot(data = deduped.data %>% filter(WordLength==0), aes(SourceName)) + 
    geom_histogram(stat = 'count') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Low Word Count Articles: Sources

```{r WordCount - low count sources}
ggplot(data = deduped.data %>% filter(WordLength<100 & WordLength!= 0), aes(SourceName)) + geom_histogram(stat = 'count') + theme(axis.ticks=element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) + labs(y = "all sources", caption = "All low count sources")

ggplot(data = deduped.data %>% filter(WordLength<100 & WordLength!= 0) %>% group_by(SourceName) %>% summarise(n = n()) %>% filter(n>100) , aes(x=SourceName, y = n) )+ geom_bar(stat = 'identity') + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +labs(y = "Count", caption = "Top 5 low word count sources")
 
```
